Conflict-Driven Evolution and Urban Development

### 2023-06-29 paper/slides.tex
Updates from Overleaf
#33 finish motivation slides

}
\usepackage{graphicx} % we need this so we can add figures
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{natbib} % we need this so we can use citation and bib properly
\usepackage{hyperref} % allows you to add hyperlink
\usepackage{amsmath} % allows you to use most mathematical features
\usepackage{setspace} % allows you to change the line spacing
\usepackage{longtable}
\usepackage{xr}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage{ragged2e}

@@

@@

@@

\begin{frame}
\frametitle{Summary:}
\justifying
\begin{itemize}
\item \textbf{Research Question}: It should be a question, not a statement here. If you think the author has asked multiple questions, pick up to three important ones. 
\item \textbf{Main Methods}: Briefly mention their main identification strategy. What data did they use. 
\item \textbf{Main findings}: pick up to three findings. You can use key numbers here if you think they are important. Like this policy has reduced 10\% pollution.(Just an example)
\end{itemize}

>>>>

}
\usepackage{graphicx} % we need this so we can add figures
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{natbib} % we need this so we can use citation and bib properly
\usepackage{hyperref} % allows you to add hyperlink
\usepackage{amsmath} % allows you to use most mathematical features
\usepackage{setspace} % allows you to change the line spacing
\usepackage{longtable}
\usepackage{xr}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage{ragged2e}
\usepackage{caption}
\usepackage{subcaption} % for subfigures

@@

\begin{itemize}
    \item Great Divergence: Europe vs. China and the rest
    \item One difference: balance of power, competition between states
\end{itemize}

% the motivation needs to be clear even when the audience doesn't know yet what the question is!

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{paper/output/slides/map_terrs_1300.png}
         \caption{1300}
         \label{fig:map1300}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{paper/output/slides/map_terrs_1800.png}
         \caption{1800}
         \label{fig:map1800}
     \end{subfigure}
    \hfill
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{paper/output/slides/map_terrs_1917.png}
         \caption{1917}
         \label{fig:map1917}
     \end{subfigure}
        \caption{Territorial history of the German Empire}
        \label{fig:terrmaps}
\end{figure}

@@

\begin{itemize}
    \item states struggle for resources (=territory)
    \item some states survive and grow, others get eaten
   \item survival of the fittest: selection for strength / power\footnote[frame,1]{\cite{levine2021}}
\end{itemize}

@@

\begin{frame}
\frametitle{This paper}
\justifying
$\rightarrow$ \textbf{Question}: 
Did this process play a role in the rise of Europe?
\medskip
\begin{itemize}
\item Wars = weak states getting eaten by better ones
\item Maybe "stronger" states are richer (institutions?) 
\item Darwinian selection caused state quality in Europe to constantly improve
\end{itemize}
